\vspace{30mm} {\Large\bf RISC-V Duo-PLIC for the Advancced Interrupt Architecture} \\ {\large Document Version \DuoPLICRev}

### 2023-06-11 doc/src/CSRs.tex
Clarify exception rules for sireg, vsireg
Signed-off-by: John Hauser <31252952+jhauser-us@users.noreply.github.com>

@@

Following the default rules for the hypervisor extension, attempts
from \mbox{VS-mode} to directly access a hypervisor or VS CSR, or
from \mbox{VU-mode} to access any supervisor-level CSR (including
hypervisor and VS CSRs), usually raise not an illegal instruction
exception but instead a virtual instruction exception.
For details, see the {\RISCV} Privileged Architecture.

%-----------------------------------------------------------------------
\section{Access control by the state-enable CSRs}

>>>>

For alias CSRs \z{sireg} and \z{vsireg}, the hypervisor extension's
usual rules for when to raise a virtual instruction exception (based
on whether an instruction is \emph{HS-qualified}) are not applicable.

The rules for \z{sireg} and \z{vsireg} in this section assume
\z{vsiselect} is accessible from \mbox{HS-mode} as usual.
See Section~\ref{sec:CSRs-stateen} for when
\z{vsiselect} may not be accessible from \mbox{HS-mode}.

All attempts to access \z{vsireg} from \mbox{VS-mode}
or \mbox{VU-mode} raise a virtual instruction exception.

@@

Following the default rules for the hypervisor extension, attempts
from \mbox{VS-mode} to directly access a hypervisor or VS CSR
other than \z{vsireg}, or from \mbox{VU-mode} to access any
supervisor-level CSR (including hypervisor and VS CSRs) other than
\z{sireg} or \z{vsireg}, usually raise not an illegal instruction
exception but instead a virtual instruction exception.
For details, see the {\RISCV} Privileged Architecture.

For \z{sireg} and \z{vsireg}, see both the previous section,
\ref{ch:CSRs-hypervisor}, and the next, \ref{sec:CSRs-stateen},
for when a virtual instruction exception is required
instead of an illegal instruction exception.

%-----------------------------------------------------------------------
\section{Access control by the state-enable CSRs}
\label{sec:CSRs-stateen}
